Alex Popescu - Final Stats

### 2024-02-01 Data & Scripts/Alex Popescu - Final Stats.Rmd
Feb 1
Eyyyyy Methods and results sent in again. Work on the discussion outline.

tab_model(PTWY.MODELS
          , pred.labels = labs.ptwy
                  , show.re.var = T
                  , show.se = T
                  , show.stat = T
                  , digits = 4
                  , title = ""
                  , dv.labels = c("Foraging to Alert"
                                  , "Foraging to Peck"
                                  , "Alert to Foraging"
                                  , "Peck to Alert")
          )
```
```{r Save PTWY Table, include = F}
webshot("PTWY_Table.html", "PTWY_Table.png")
```

>>>>

tab_model(PTWY.MODELS
          , pred.labels = labs.ptwy
                  , show.re.var = T
                  , show.se = T
                  , show.stat = T
                  , digits = 4
                  , title = ""
                  , dv.labels = c("Foraging to Alert"
                                  , "Foraging to Peck"
                                  , "Alert to Foraging"
                                  , "Peck to Alert")
          , file = "PTWY_Table.html"
          )
```
```{r Save PTWY Table, include = F}
webshot("PTWY_Table.html", "PTWY_Table.png")
```
